%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} 

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Alex Minnaar} % Your name
\address{41 Mathersfield Dr. \\ Toronto, Ontario, Canada} % Your address
\address{cell: (647) 629-0280 \\ home: (416) 488-0895 \\ minnaaralex@gmail.com \\ alexminnaar.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University College London} \hfill {\em November 2012} \\ 
MSc in Computational Statistics \& Machine Learning \\
London, United Kingdom

{\bf Queen's University} \hfill {\em June 2011} \\ 
BSc in Mathematics \& Engineering - Control and Computing stream \\
Kingston, Ontario, Canada

{\bf Upper Canada College} \hfill {\em June 2007} \\ 
Ontario Diploma \& International Baccalaureate Diploma \\
Toronto, Ontario, Canada\\ 

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{VerticalScope, Inc}{March 2014 - Present}{Software Engineer}{Toronto, Ontario, Canada}
\item Part of the Data Science team. Building large-scale, real-time natural language processing applications with unstructured social media data.
\item Implementing NLP/machine learning concepts such as named entity recognition/disambiguation, topic modeling, sentiment analysis, and recommender systems.
\item Using the Scala programming language with technologies such as Spark, Kafka, Elasticsearch and Cassandra.
\end{rSubsection}


\begin{rSubsection}{Tucows, Inc}{February 2013 - March 2014}{Data Scientist}{Toronto, Ontario, Canada}
\item Implemented statistical analysis to gain insight on customer churn.
\item Developed several machine learning applications involving classification, clustering, collaborative filtering and sentiment analysis.
\item Setup company's first Hadoop cluster using Amazon ec2 and Cloudera.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Advanced Algos, Inc}{October 2012 - December 2012}{Data Analyst Intern}{Toronto, Ontario, Canada}
\item Performed data analysis tasks on CME and EBS data sets from Spot and FX markets.
\item Wrote C++ programs to search for specific occurrences in large data sets.

\end{rSubsection}

%------------------------------------------------



\end{rSection}

\newpage
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Research and Project Experience}

\begin{rSubsection}{MSc Thesis}{University College London}{New Methods for Identifying Small Mean-reverting Portfolios}{}
\item Studying the portfolio selection problem of extracting optimally mean-reverting portfolios from multi-
variate time-series datasets while constraining the number of assets in the portfolio. Included comparison of approximation techniques such as greedy search, semi-definite relaxation, and genetic algorithms.
Presents novel on-line learning algorithm that dynamically adjusts portfolio weights to achieve optimal
mean-reversion.
\end{rSubsection}

\begin{rSubsection}{Mathematical Programming and Research Methods}{University College London}{}{}
\item Implementation of machine learning techniques in Matlab and Mathematica. These include gradient
descent, linear/polynomial regression, kernel methods, perceptron algorithm, k-means clustering, PCA,
and classification via SVMs.
\end{rSubsection}

\begin{rSubsection}{Heritage Health Prize Kaggle Competition}{}{}{}
\item Competition in which contestants are given a training set of hospital patient data to build algorithms
that predict the number of days a group of patients will spend in hospital for a given test set. Best
results came from tree-based algorithms and boosting. Scored in top 75 out of 1300+ teams.
\end{rSubsection}

\begin{rSubsection}{Undergraduate Thesis}{Queen's University}{Stochastic Systems with Data Rate Constraints}{}
\item A dynamical system was studied in which two noisy sensors are connected to a controller through a
noiseless finite capacity channel. A stability result was presented in the case where the eigenvalues of
the system matrix are real and distinct. A policy that achieves stochastic stability is also presented
and is shown to asymptotically achieve the minimum average rate for the communication channel. \\
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths and Achievements}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages & C++, Java/Scala, Python, Javascript/JQuery.  \\ \\
Statistical Software & Matlab, R.\\ \\
Databases & MySQL, Elasticsearch, Cassandra. \\ \\
Hadoop \& Big Data & MapReduce programming, Hive, Mahout, Spark. \\ \\
Awards & Ontario Scholar.\\ & Upper Canada College Prefect.\\ & Euclid Math Contest Certificate of Distinction.\\ \\
Certificates & Hadoop Fundamentals Certificate, \textit{BigDataUniversity.com}.\\
& C++ for Financial Engineering, \textit{Baruch College}.\\ \\
Personal Projects & alexminnaar.com (blog), github.com/alexminnaar (open source projects). \\ \\
Interests & Brazilian Jiu-Jitsu, CrossFit, Music, Movies.
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
